Maintenance planning on French military aircraft operations

### 2018-09-20 R/presentations/CLAIO_presentation/presentation.Rmd
experiments of MOSIM instances with new model. updated CLAIO ppt with new images. New R code for images.

---
title: "Maintenance planning on French military aircraft operations"
author: |
    | Franco Peschiera, Alain Haït, Olga Battaïa, Nicolas Dupin
institute: "ISAE SUPAERO"
date: "September 24, 2018"
output: 
  slidy_presentation:
    css: ./../../../css/baobab_slidy.css
    incremental: yes
    footer: "ISAE-SUPAERO, Université de Toulouse, France"
    # slide_level: 2
    # toc: true
  beamer_presentation:
    theme: "Berlin"
    toc: true
    slide_level: 2
    incremental: yes
    fig_height: 4
    # citation_package: natbib
    # footer: "ISAE-SUPAERO, Université de Toulouse, France"
    includes:
        in_header: header.tex
bibliography: MFMP_NRP.bib
# nocite: '@*'
editor_options: 
  chunk_output_type: console
---

@@

Assign both missions and maintenance operations to a fleet of aircraft in order to maximize availability and minimize costs. Missions have fixed start and end times and have particular needs in terms of aircraft and time.

@@

* FMP: Flight and Maintenance Planning problem.
* A series of $j \in \mathcal{J}$ tasks are planned along a horizon divided into $t \in \mathcal{T}$ periods. Since all tasks are already scheduled, we know time periods $T_j \subset \mathcal{T}$ in which they will be realized. 
* Each task requires a certain number $R_{j}$ of resources $i \in \mathcal{I}$ which it employs for a time duration defined by $H_j$ in each period and needs to be assigned for a minimum of $MT_j$ consecutive periods if assigned.
* Resources require recurrent preventive maintenance operations since the realization of tasks diminish their remaining usage time.
* A maintenance operation takes exactly $m$ periods and cannot be interrupted. It restores the resource's remaining usage time to exactly $H^M$ units.

@@

* Asignments to missions are done instead of assignments of flight hours.
* Missions need to be assigned for a minimal duration.
* This model also features several improvements in the MIP modelling that permit greater instance sizes.

@@

@@

\begin{align}
    & m_{it'} + m_{it} \leq 1
      & t \in \mathcal{T}, t' \in \mathcal{T}^{m}_t, i \in \mathcal{I}\label{eq:ret_min}\\ 
    & \sum_{t' \in \mathcal{T}^{M}_t} m_{it'} \geq  m_{it}
      & t \in \mathcal{T}, i \in \mathcal{I}\label{eq:ret_max}\\
    & m_{it} = 0
      & t \in \mathcal{T}^{m_{ini}}_i, i \in \mathcal{I}\label{eq:ret_min_init} \\
    & \sum_{t \in \mathcal{T}^{M_{ini}}_i} m_{it} \geq  1 
      & i \in \mathcal{I}\label{eq:ret_max_init}
\end{align}

Maintenances cannot executed too soon or too late with respect to the previous one.

@@

@@

@@

* Small instances have **30.000 variables** and **20.000 constraints**.
* Medium instances have **80.000 variables** and **50.000 constraints**.
* Runs of 30 minutes have been done on 30 randomly generated cases per scenario.
* CPLEX was used in an i7, quadcore Ubuntu 18.04 workstation.

@@

* `r infeasible[1]`% of instances were proved infeasible inmediately.
* From feasible small instances, a mean gap of `r scen_means[1]`% was found after 30 min.
* From feasible medium instances, a mean gap of `r scen_means[2]`% was found after 30 min.

>>>>

---
title: "Maintenance planning on French military aircraft operations"
author: |
    | Franco Peschiera, Alain Haït, Olga Battaïa, Nicolas Dupin
institute: "ISAE-SUPAERO, Université de Toulouse, France"
date: "September 24, 2018"
output: 
  beamer_presentation:
    # keep_tex: true
    theme: "Berlin"
    toc: true
    slide_level: 2
    incremental: yes
    fig_height: 4
    # citation_package: natbib
    # footer: "ISAE-SUPAERO, Université de Toulouse, France"
    includes:
        in_header: header.tex
    # before_body: before_body.tex
  slidy_presentation:
    css: ./../../../css/baobab_slidy.css
    incremental: yes
    footer: "ISAE-SUPAERO, Université de Toulouse, France"
    # slide_level: 2
    # toc: true
bibliography: MFMP_NRP.bib
# nocite: '@*'
editor_options: 
  chunk_output_type: console
---

@@

**Assign** both **missions and maintenance** operations to a fleet of **aircraft** in order to maximize **availability** and minimize **costs**. **Missions** have **fixed** start and end times and have particular **needs** in terms of aircraft and time.

@@

* FMP: Flight and Maintenance Planning problem.
* A series of $j \in \mathcal{J}$ tasks are planned along a horizon divided into $t \in \mathcal{T}$ periods.
* Each task requires $R_{j}$ of resources for $H_j$ hours and needs to be assigned for a minimum of $MT_j$ consecutive periods.
* Resources $i \in \mathcal{I}$ require recurrent preventive maintenance operations.
* A maintenance operation takes exactly $m$ periods and restores the resource's remaining usage time to exactly $H^M$ units.

@@

* Asignments to missions are done instead of assignments of flight hours.
* Missions need to be assigned for a minimal duration.
* Because of these differences, a new model is proposed to deal with this new problem.

@@

## Model: variables

The following variables are used in the model.

\begin{tabular}{lll}
$m_{it}$    &: maintenance start &  $|\mathcal{I}| \times |\mathcal{T}|$ \\
$a_{jti}$   &: task assignment &  $|\mathcal{T}| \times |\mathcal{J}_t| \times |\mathcal{I}_j|$ \\
$a^s_{jti}$ &: task assignment start &  $|\mathcal{T}| \times |\mathcal{J}_t| \times |\mathcal{I}_j|$ \\
$u_{it}$    &: monthly usage time &  $|\mathcal{I}| \times |\mathcal{T}|$ \\
$rut_{it}$  &: remaining usage time &  $|\mathcal{I}| \times |\mathcal{T}|$ \\
\end{tabular}

@@

\begin{align}
    & m_{it'} + m_{it} \leq 1
      & t \in \mathcal{T}, t' \in \mathcal{T}^{m}_t, i \in \mathcal{I}\label{eq:ret_min}\\ 
    & \sum_{t' \in \mathcal{T}^{M}_t} m_{it'} \geq  m_{it}
      & t \in \mathcal{T}, i \in \mathcal{I}\label{eq:ret_max}
\end{align}

<!-- Maintenances cannot executed too soon or too late with respect to the previous one. -->

```{r, echo=FALSE, out.width='60%', fig.align="center"}
'../img/rut_ret.png' %>% 
    paste0(path_to_R_dir, .) %>%
    knitr::include_graphics()
```

@@

## Example of a solution

```{r, echo=FALSE, out.width='100%', fig.align="center"}
'../img/example_solution1.png' %>% 
    paste0(path_to_R_dir, .) %>%
    knitr::include_graphics()
```

## Results on previous instances

All instances are solved to 0.02% of optimality in less than one hour. Previously this was not the case.

\begin{tabular}{lrrrr}
   id &  objective &  gap (\%) &  time (s) &      bound \\
 I\_0 & 2212136.80 &      0.01 &     29.79 & 2211841.38 \\
 I\_1 & 4508365.88 &      0.02 &    173.11 & 4507542.47 \\
 I\_2 & 6208008.67 &      0.02 &    409.66 & 6206896.17 \\
 I\_3 & 7511314.89 &      0.03 &    836.08 & 7509070.16 \\
 I\_4 & 2217358.08 &      0.02 &     37.66 & 2216944.92 \\
 I\_5 & 4517690.48 &      0.01 &    208.25 & 4517191.09 \\
 I\_6 & 6220420.49 &      0.01 &    331.90 & 6219541.67 \\
 I\_7 & 7526281.03 &      0.02 &   1731.50 & 7524413.60 \\
 I\_8 & 2228684.87 &      0.01 &     76.18 & 2228481.13 \\
 I\_9 & 4538717.82 &      0.02 &   3332.95 & 4537837.14 \\
\end{tabular}

@@

Random instances were generated to test the performance following the known instances guidelines.

@@

* Small instances have **30.000 variables** and **20.000 constraints**.
* Large instances have **80.000 variables** and **50.000 constraints**.
* Runs of 30 minutes have been done on 30 randomly generated cases per scenario.
* CPLEX was used in an i7, quadcore Ubuntu 18.04 workstation.

@@

* From feasible small instances, a mean gap of `r scen_means[1]`% was found after 30 min.
* From feasible large instances, a mean gap of `r scen_means[2]`% was found after 30 min.
